A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Add pagebreak before conclusion.
Clean table

\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$RandomRecommender$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$PopularityRecommender$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMapRecommender$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModelRecommender$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBasedRecommender$ & .014 & .020 & .016 & .115 & .186 & .142 \\ \hline
$NeighborhoodRecommneder$ & .040 & .060 & .048 & .137 & .240 & .175 \\ \hline
$LatentFeatureRecommender$ & .036 & .060 & .045 & .174 & .228 & .197 \\ \hline

>>>>

\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
